Malacology: A Programmable Storage System

### 2016-10-15 paper/paper.tex

These three trends put evolutionary pressure on storage systems and raise the
question of whether there are principles that storage systems designers can follow
to evolve storage systems efficiently and without jeopardizing years of
code-hardening and performance optimization efforts that are important for
users to continue to entrust their data to the storage system.

In this paper we investigate an approach that focuses on generalizing and
composing existing
storage system resources, services, and abstractions that in a generalized form
can be used to \emph{program} new services. By composing higher-level services
over existing abstraction one can reuse
subsystems and leverage their optimizations, established correctness,
robustness, and efficiency. We will refer to this programmability as
\emph{programmable storage}, which differs from \emph{active storage} (the
injection and execution of arbitrary code in a storage system) and
\emph{software-defined storage} (the control of thin-provisioning of storage).

@@

{\it \textbf{The definition a programmable storage system}} to be ``a storage
system that allows existing abstractions to be re-used and composed to form
new data and metadata management services whose operation is orothogonal to
system correctness".  Our prototype includes (but is not limited to) the
following building blocks:

>>>>

These three trends put evolutionary pressure on storage systems and raise the
question of whether there are principles that storage systems designers can follow
to evolve storage systems efficiently, without jeopardizing years of
code-hardening and performance optimization efforts.
% that are important for
%users to continue to entrust their data to the storage system.

In this paper we investigate an approach that focuses on generalizing and
composing existing
storage system resources, services, and abstractions that in a generalized form
can be used to \emph{program} new services. By composing higher-level services
over existing abstraction one can reuse
subsystems and leverage their optimizations, established correctness,
robustness, and efficiency. 
%We will refer to this programmability as
%\emph{programmable storage}, which differs from \emph{active storage} (the
%injection and execution of arbitrary code in a storage system) 
%and
%\emph{software-defined storage} (the control of thin-provisioning of storage).

{\it \textbf{We define a programmable storage system}} to be a storage system that facilitates the 
re-use and extension of existing storage abstractions and services provided by the underlying software stack,
to enable the creation of new storage abstractions via composition.
A programmable storage system is realized by exposing existing functionality (such as 
metadata services and synchronization capabilities) as interfaces that can be ``glued together''
using a high-level language.  Programmable storage differs from \emph{active storage},
or the injection and execution of arbitrary code in a storage system.

@@

Our prototype includes a non-exhaustive set of interfaces that can be used as building blocks
for constructing novel storage abstractions, including:
